\Large{Adversarial Variational Optimization of Non-Differentiable Simulators}

### 2017-07-13 tex/paper.tex
layout

As thoroughly explored in \citep{2017arXiv170104862A}, GANs remain remarkably
difficult to train because of vanishing gradients as $d$ saturates, or because of
unreliable updates when the training procedure is relaxed. As a remedy,
Wasserstein GANs~\citep{2017arXiv170107875A} reformulate the adversarial
setup in order to minimize the Wasserstein-1 distance $W(p_r(\mathbf{x}), p(\mathbf{x}|\bftheta))$ by
replacing the adversarial classifier with a 1-Lipschitz adversarial critic
$d(\cdot; \bfphi) : \mathbb{R}^d \to \mathbb{R}$.
\begin{align}
W( p_r(\mathbf{x} ), p(\mathbf{x} | \bftheta)  ) =& \sup_{\bfphi} \mathbb{E}_{p(\tilde{\mathbf{x}}|\bftheta)} [d(\tilde{\mathbf{x}})] - \mathbb{E}_{p_r(\mathbf{x})} [d(\mathbf{x})] \\
\equiv& \sup_{\bfphi} \mathcal{L}_W
\end{align}
Under the WGAN-GP formulation of \cite{2017arXiv170400028G}
for stabilizing the optimization procedure,
training $d$ and $g$ results in alternating gradient updates on $\bfphi$ and $\bftheta$ in order to respectively minimize
\begin{align}
    {\cal L}_d =\,&  \mathcal{L}_W + \lambda \mathbb{E}_{\hat{\mathbf{x}} \sim p({\hat{\mathbf{x}})}} [(|| \nabla_{\hat{\mathbf{x}}} d({\hat{\mathbf{x}}};\bfphi) ||_2 - 1)^2] \\
    {\cal L}_g =\,& - \mathcal{L}_W
\end{align}
%
%\begin{align}
%    {\cal L}_d =\,&  {\cal L}_W + \lambda \mathbb{E}_{\hat{\mathbf{x}} \sim p({\hat{\mathbf{x}})}} [(|| \nabla_{\hat{\mathbf{x}}} d({\hat{\mathbf{x}}};\bfphi) ||_2 - 1)^2] \\
%    {\cal L}_g =\,& - {\cal L}_W
%\end{align}
%\begin{align}
%    {\cal L}_d =\,& \mathbb{E}_{\tilde{\mathbf{x}} \sim p(\mathbf{x}|\bftheta)} [d(\tilde{\mathbf{x}};\bfphi)] - \mathbb{E}_{\mathbf{x} \sim p_r(\mathbf{x})} [d(\mathbf{x};\bfphi)]  \nonumber \\
%                  & + \lambda \mathbb{E}_{\hat{\mathbf{x}} \sim p({\hat{\mathbf{x}})}} [(|| \nabla_{\hat{\mathbf{x}}} d({\hat{\mathbf{x}}};\bfphi) ||_2 - 1)^2] \\
%    {\cal L}_g =\,& -\mathbb{E}_{\tilde{\mathbf{x}} \sim p(\mathbf{x}|\bftheta)} [d(\tilde{\mathbf{x}};\bfphi)]
%\end{align}
where ${\hat{\mathbf{x}}} := \epsilon \mathbf{x} +
(1-\epsilon)\tilde{\mathbf{x}}$, for $\epsilon \sim U[0,1]$, $\mathbf{x} \sim
p_r(\mathbf{x})$ and $\tilde{\mathbf{x}} \sim p(\mathbf{x}|\bftheta)$.

@@

\subsection{Adversarial variational inference through model criticism}

>>>>

As thoroughly explored in \citep{2017arXiv170104862A}, GANs remain remarkably
difficult to train because of vanishing gradients as $d$ saturates, or because of
unreliable updates when the training procedure is relaxed. As a remedy,
Wasserstein GANs~\citep{2017arXiv170107875A} reformulate the adversarial
setup in order to minimize the Wasserstein-1 distance $W( p_r(\mathbf{x} ), p(\mathbf{x} | \bftheta)  )$
by replacing the adversarial classifier with a 1-Lipschitz adversarial critic
$d(\cdot; \bfphi) : \mathbb{R}^d \to \mathbb{R}$, and where
\begin{align}
& W( p_r(\mathbf{x} ), p(\mathbf{x} | \bftheta)  ) \nonumber \\
&= \sup_{\bfphi}  \mathbb{E}_{\tilde{\mathbf{x}}\sim p(\mathbf{x}|\bftheta)} [d(\tilde{\mathbf{x}}; \bfphi)] - \mathbb{E}_{\mathbf{x} \sim p_r(\mathbf{x})} [d(\mathbf{x}; \bfphi)] \nonumber \\
&\equiv \sup_{\bfphi} \mathcal{L}_W.
\end{align}
Under the WGAN-GP formulation of \cite{2017arXiv170400028G}
for stabilizing the optimization procedure,
training $d$ and $g$ results in alternating gradient updates on $\bfphi$ and $\bftheta$ in order to respectively minimize
\begin{align}
    {\cal L}_d =\,&  \mathcal{L}_W + \lambda \mathbb{E}_{\hat{\mathbf{x}} \sim p({\hat{\mathbf{x}})}} [(|| \nabla_{\hat{\mathbf{x}}} d({\hat{\mathbf{x}}};\bfphi) ||_2 - 1)^2] \\
    {\cal L}_g =\,& - \mathcal{L}_W
\end{align}
%
%\begin{align}
%    {\cal L}_d =\,&  {\cal L}_W + \lambda \mathbb{E}_{\hat{\mathbf{x}} \sim p({\hat{\mathbf{x}})}} [(|| \nabla_{\hat{\mathbf{x}}} d({\hat{\mathbf{x}}};\bfphi) ||_2 - 1)^2] \\
%    {\cal L}_g =\,& - {\cal L}_W
%\end{align}
%\begin{align}
%    {\cal L}_d =\,& \mathbb{E}_{\tilde{\mathbf{x}} \sim p(\mathbf{x}|\bftheta)} [d(\tilde{\mathbf{x}};\bfphi)] - \mathbb{E}_{\mathbf{x} \sim p_r(\mathbf{x})} [d(\mathbf{x};\bfphi)]  \nonumber \\
%                  & + \lambda \mathbb{E}_{\hat{\mathbf{x}} \sim p({\hat{\mathbf{x}})}} [(|| \nabla_{\hat{\mathbf{x}}} d({\hat{\mathbf{x}}};\bfphi) ||_2 - 1)^2] \\
%    {\cal L}_g =\,& -\mathbb{E}_{\tilde{\mathbf{x}} \sim p(\mathbf{x}|\bftheta)} [d(\tilde{\mathbf{x}};\bfphi)]
%\end{align}
where ${\hat{\mathbf{x}}} := \epsilon \mathbf{x} +
(1-\epsilon)\tilde{\mathbf{x}}$, for $\epsilon \sim U[0,1]$, $\mathbf{x} \sim
p_r(\mathbf{x})$ and $\tilde{\mathbf{x}} \sim p(\mathbf{x}|\bftheta)$.

@@

\subsection{Adversarial variational inference\\
            through model criticism}
